Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
question about model

\TODO{Is the following paragraph best suited here? It describes an
  assumption that we make about commands, to guarantee the validity of
  our transformations. The assumption is needed due to the limitation
  of the programming model of one input one output per command.}

@@

In order to adequately utilize the available computational resources,
a distributed implementation should exploit data parallelism. Data
parallelism is based on the observation that some operations produce
the same result when performed independently on subsets of the input
data, merging the results afterwards. This is the basic optimization
that is used by popular distributed processing systems such as
MapReduce \cite{DG2004MR} and Apache Spark\cite{spark:12}. Unfortunately, the
dataflow graph model of most of these systems is not expressive enough
to represent data parallelism \km{not sure this is true}, so the distributed implementations that
they perform do not preserve the semantics of their dataflow model.

@@

>>>>

\TODO{Is the following paragraph best suited here? It describes an
  assumption that we make about commands, to guarantee the validity of
  our transformations. The assumption is needed due to the limitation
  of the programming model of one input one output per command.}pldi

@@

In order to adequately utilize the available computational resources,
a distributed implementation should exploit data parallelism. Data
parallelism is based on the observation that some operations produce
the same result when performed independently on subsets of the input
data, merging the results afterwards. This is the basic optimization
that is used by popular distributed processing systems such as
MapReduce \cite{DG2004MR} and Apache Spark \cite{spark:12}. Unfortunately, the
dataflow graph model of most of these systems is not expressive enough
to represent data parallelism \km{not sure this is true}, so the distributed implementations that
they perform do not preserve the semantics of their dataflow model.

@@

\km{This is a nice characterization, which I think is true in most settings. There is a caveat though: You can have stateless programs that emit output when they start (before they consume the stream) and/or when they consume the EOF symbol. In this case I am not sure the equation above holds.}
